### 2023-08-22 application.tex
up

\begin{theorem}{}
{\sc Resilience} is decidable for VASS when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for lossy counter machines when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

>>>>

\begin{theorem}\label{SL VASS}
{\sc Resilience} is decidable for VASS when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}\label{SL Lossy}
{\sc Resilience} is decidable for lossy counter machines when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}\label{SL int-VASS}
{\sc Resilience} is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

Remark that
Theorem~\ref{SL Lossy} and
Theorem~\ref{SL int-VASS}
(resp. Theorem~\ref{RP VASS})
did not make use of the hypothesis that $\Bad$ is the complement of $\Safe$, simply relying on the
semilinearity of the set (resp. its definability in the existential theory of the rationals with addition and order). Thus 
the mentionned theorems still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.
